MPA Gap Analysis: IUCN and AquaMaps

### 2016-02-25 mpa_analysis/wdpa_prep.Rmd
got the mpa analysis going well.

library(rgdal)
library(maptools)
library(raster)
library(readr)
library(tidyr)
library(dplyr)
library(stringr)

@@

### When knitting this, it automatically sets WD to be this directory...
### the 'setwd()' is there for running by chunk
```

  prot_code_df <- data.frame('IUCN_CAT'  = c('I', 'Ia', 'Ib', 'II', 'III', 'IV', 'V', 'VI'),
                             'prot_code' = c(  1,   1,    1,    2,     3,    4,   5,    6))
# poly_wdpa_save <- poly_wdpa
  poly_wdpa@data <- poly_wdpa@data %>%
    left_join(prot_code_df, by = 'IUCN_CAT') %>%
    mutate(prot_code = ifelse(is.na(prot_code), 7, prot_code))

  writeOGR(poly_mpa, dsn = dir_wdpa, layer = lyr_mpa,
           driver = 'ESRI Shapefile')
  writeOGR(poly_mpa_marine, dsn = dir_wdpa, layer = lyr_mpa_mar,
           driver = 'ESRI Shapefile')
}

poly_mpa <- readOGR(dir_wdpa, lyr_mpa, stringsAsFactors = FALSE)
### create simplified polygon
polys_mpa_area <- lapply(poly_mpa@polygons, function(x) x@area)
poly_mpa1 <- poly_mpa[polys_mpa_area > 1e-5, ]
poly_mpa1 <- poly_simplify(poly_mpa1, thresh = 1e-5, verbose = TRUE)

### sort by STATUS_YR, descending, so gdal_rasterize will assign newer
### values then overwrite (where applicable) with older values
poly_mpa2 <- poly_mpa1[order(z <- poly_mpa1@data$STATUS_YR, decreasing = TRUE), ]

writeOGR(poly_mpa1, dsn = dir_wdpa,
         layer = paste(lyr_mpa, '1', sep = ''),
         driver = 'ESRI Shapefile')

}
```

ptm <- proc.time()
raster::writeRaster(tmp_rast, fnl_dst, overwrite = TRUE)
message('Write ', src, '\n  to ', fnl_dst, '; \n  ', round((proc.time() - ptm)[3], 2), ' seconds')
remove(tmp_rast)
unlink(tmp_dst)

@@

>>>>

library(rgdal)
library(raster)
library(readr)
library(tidyr)
library(dplyr)
library(stringr)

@@

### When knitting this, it automatically sets WD to be this directory...
### the 'setwd()' is there for running by chunk

p4s_wgs84 <- '+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0'
crs_wgs84 <- CRS(p4s_wgs84)

@@

  prot_code_df <- data.frame('IUCN_CAT'  = c('Ia', 'Ib', 'II', 'III', 'IV', 'V', 'VI'),
                             'prot_code' = c(  1,    1,    2,     3,    4,   5,    6))
# poly_wdpa_save <- poly_wdpa
  poly_wdpa@data <- poly_wdpa@data %>%
    left_join(prot_code_df, by = 'IUCN_CAT') %>%
    mutate(prot_code = ifelse(is.na(prot_code), 7, prot_code))

  writeOGR(poly_mpa, dsn = dir_wdpa, layer = lyr_mpa,
           driver = 'ESRI Shapefile', overwrite_layer = TRUE)
  writeOGR(poly_mpa_marine, dsn = dir_wdpa, layer = lyr_mpa_mar,
           driver = 'ESRI Shapefile', overwrite_layer = TRUE)
}

poly_mpa <- readOGR(dir_wdpa, lyr_mpa, stringsAsFactors = FALSE)
# poly_mpa <- readShapePoly(fn = file.path(dir_wdpa, lyr_mpa),
#                           proj4string = crs_wgs84,
#                           stringsAsFactors = FALSE)

### create simplified polygon
polys_mpa_area <- lapply(poly_mpa@polygons, function(x) x@area)
poly_mpa1 <- poly_mpa[polys_mpa_area > 1e-5, ]
poly_mpa1 <- poly_simplify(poly_mpa1, thresh = 1e-5, verbose = TRUE)

### sort by STATUS_YR, descending, so gdal_rasterize will assign newer
### values then overwrite (where applicable) with older values
poly_mpa1 <- poly_mpa1[order(poly_mpa1@data$STATUS_YR, decreasing = TRUE), ]

# writeOGR(poly_mpa1, dsn = dir_wdpa,
#          layer = paste(lyr_mpa, '1', sep = ''),
#          driver = 'ESRI Shapefile')
maptools::writePolyShape(poly_mpa1, 
                         fn = file.path(dir_wdpa, paste(lyr_mpa, '1', sep = '')))
### copy .prj:
file.copy(from = file.path(dir_wdpa, paste(lyr_mpa, '.prj', sep = '')), 
          to = file.path(dir_wdpa, paste(lyr_mpa, '1.prj', sep = '')))

ptm <- proc.time()
raster::writeRaster(tmp_rast, fnl_dst, 
                    progress = 'text', overwrite = TRUE)
message('Write ', src, '\n  to ', fnl_dst, '; \n  ', round((proc.time() - ptm)[3], 2), ' seconds')
remove(tmp_rast)
unlink(tmp_dst)
